PWD.KAZ

### 2019-07-17 results/PWD.KAZ.BivData.Rmd
tried fitting exponential model

#SC.test <- t.test()

@@

newPWD_curate_BivData =
  read.csv("~./MLH1repo/data/BivData/Merged_Curate_PWD_BivData.csv", header = TRUE)

#update these dataframes!
#isolate the passing foci 
curBivData_PWD.good.foci  <- newPWD_curate_BivData[newPWD_curate_BivData$foci.pass == 1,]

@@

table(newPWD_curate_BivData$fileName)
table(newPWD_curate_BivData$mouse) #4 mice, ~100 each mouse

@@

```{r curated, echo=FALSE}
curBivData_KAZ.good.foci <- curBivData_KAZ[curBivData_KAZ$foci.pass == 1,]
#curated objects
KAZ_m2_curate_bivData =
  read.csv("~./MLH1repo/data/BivData/curated_21may18_KAZ_m2_BivData.csv", header = TRUE)

@@

@@

#melt KAZ
#isolate the passing foci 
curBivData_KAZ.good.foci  <- curBivData_KAZ[curBivData_KAZ$foci.pass == 1,]
#colnames(curBivData_KAZ)

```{r plot}

library(ggplot2)
library(plyr)

nPWD.obs <- ddply(.data=curBivData_PWD.melt, 
                 .(hand.foci.count),
                 summarize, 
                 n=paste("n =", length(unique(Obj.ID))))

#normalized foci plots
PWD.plot.nrm <- ggplot(curBivData_PWD.melt,
              aes(x=Foci.nrm.pos, fill=Foci.Type.nrm) ) + 
  geom_histogram(alpha= 0.5,stat = "bin", position= "identity")+
 facet_wrap(~ hand.foci.count, scales="free", ncol=1)+ggtitle("norm foci position PWD")+

@@

nKAZ.obs <- ddply(.data=curBivData_KAZ.melt, 
                 .(hand.foci.count),
                 summarize, 
                 n=paste("n =", length(unique(Obj.ID))))

@@

KAZ.plot.nrm    <- ggplot(curBivData_KAZ.melt,
              aes(x=nrmFoci.pos, fill=nrmFoci.Type) ) +

@@

```{r}
#goal, examine the ages of mice being compared
#distribution of ages

histys <- ggplot(PWD.KAZ_MLH1.imprv, aes(age.weeks, fill=strain))+geom_density()

@@

```{r first.analysis, echo=FALSE}
#initial analysis of the BivData

Kaz.biv.plot <- ggplot(data = KAZ_bivData, aes(x= centromere_PER_Position, y=chromosomeLength) )+geom_point()

@@

Above is merged curated data from PWD and KAZ males of similar ages

>>>>

OneCO <- all.curated.BivData[all.curated.BivData$hand.foci.count == 1,]
TwoCO <- all.curated.BivData[all.curated.BivData$hand.foci.count == 2,]

Class.SC.test.1CO <- t.test(OneCO$chromosomeLength[OneCO$strain == "PWD"], OneCO$chromosomeLength[OneCO$strain == "KAZ"])

Class.SC.test.2CO <- t.test(TwoCO$chromosomeLength[TwoCO$strain == "PWD"],TwoCO$chromosomeLength[TwoCO$strain == "KAZ"])

@@

#newPWD_curate_BivData =
#  read.csv("~./MLH1repo/data/BivData/Merged_Curate_PWD_BivData.csv", header = TRUE)

#update these dataframes!
#isolate the passing foci 
#curBivData_PWD.good.foci  <- newPWD_curate_BivData[newPWD_curate_BivData$foci.pass == 1,]

curBivData_PWD.good.foci <- PWD.auto.man_BivData[PWD.auto.man_BivData$foci.pass == 1,]

@@

#table(newPWD_curate_BivData$fileName)
#table(newPWD_curate_BivData$mouse) #4 mice, ~100 each mouse

@@

```{r melt.KAZ, echo=FALSE}

#use the combined - auto and manual data

curBivData_KAZ.good.foci <- KAZ.auto.man_BivData[KAZ.auto.man_BivData$foci.pass == 1,]
#curated objects
#KAZ_m2_curate_bivData =
#  read.csv("~./MLH1repo/data/BivData/curated_21may18_KAZ_m2_BivData.csv", header = TRUE)

@@

#melt KAZ
#isolate the passing foci 
#curBivData_KAZ.good.foci  <- curBivData_KAZ[curBivData_KAZ$foci.pass == 1,]

curBivData_KAZ.good.foci <- KAZ.auto.man_BivData[KAZ.auto.man_BivData$foci.pass == 1,]
colnames(curBivData_KAZ.good.foci)

curBivData_KAZ.good.foci$nrm.F1.pos <- curBivData_KAZ.good.foci$Foci1 / curBivData_KAZ.good.foci$chromosomeLength
curBivData_KAZ.good.foci$nrm.F2.pos <- curBivData_KAZ.good.foci$Foci2 / curBivData_KAZ.good.foci$chromosomeLength
curBivData_KAZ.good.foci$nrm.F3.pos <-   curBivData_KAZ.good.foci$Foci3 / curBivData_KAZ.good.foci$chromosomeLength

@@

```{r position.plot}
library(ggplot2)
library(plyr)

curBivData_PWD.melt <- curBivData_PWD.melt[curBivData_PWD.melt$hand.foci.count != "1?",]

curBivData_PWD.melt <- droplevels(curBivData_PWD.melt)

curBivData_PWD.melt$hand.foci.count <- as.numeric(curBivData_PWD.melt$hand.foci.count)

nPWD.obs <- ddply(.data=curBivData_PWD.melt[curBivData_PWD.melt$hand.foci.count <3,], 
                 .(hand.foci.count),
                 summarize, 
                 n=paste("n =", length(unique(Obj.ID))))

#normalized foci plots
PWD.plot.nrm <- ggplot(curBivData_PWD.melt[curBivData_PWD.melt$hand.foci.count < 3,],
              aes(x=Foci.nrm.pos, fill=Foci.Type.nrm) ) + 
  geom_histogram(alpha= 0.5,stat = "bin", position= "identity")+
 facet_wrap(~ hand.foci.count, scales="free", ncol=1)+ggtitle("norm foci position PWD")+

@@

curBivData_KAZ.melt2 <- curBivData_KAZ.melt[!is.na(curBivData_KAZ.melt$hand.foci.count),]
curBivData_KAZ.melt2 <- curBivData_KAZ.melt2[curBivData_KAZ.melt2$hand.foci.count < 3,]

nKAZ.obs <- ddply(.data=curBivData_KAZ.melt2, 
                 .(hand.foci.count),
                 summarize, 
                 n=paste("n =", length(unique(Obj.ID))))

@@

KAZ.plot.nrm    <- ggplot(curBivData_KAZ.melt2,
              aes(x=nrmFoci.pos, fill=nrmFoci.Type) ) +

@@

```{r}
#t.test of nrm positions

PWD.OneCO_nrmPos <- curBivData_PWD.melt[curBivData_PWD.melt$hand.foci.count ==1,]
PWD.TWOCO_nrmPos <- curBivData_PWD.melt[curBivData_PWD.melt$hand.foci.count ==2,]

KAZ.OneCO_nrmPos <- curBivData_KAZ.melt2[curBivData_KAZ.melt2$hand.foci.count ==1,]
KAZ.TWOCO_nrmPos <- curBivData_KAZ.melt2[curBivData_KAZ.melt2$hand.foci.count ==2,]

t.test(PWD.OneCO_nrmPos$Foci.nrm.pos, KAZ.OneCO_nrmPos$nrmFoci.pos)
#p-value = 0.5468

t.test(KAZ.TWOCO_nrmPos$nrmFoci.pos[KAZ.TWOCO_nrmPos$nrmFoci.Type == "nrm.F1.pos"],
       PWD.TWOCO_nrmPos$Foci.nrm.pos[PWD.TWOCO_nrmPos$Foci.Type.nrm == "nrm.F1"])
#p-value = 0.9421

t.test(KAZ.TWOCO_nrmPos$nrmFoci.pos[KAZ.TWOCO_nrmPos$nrmFoci.Type == "nrm.F2.pos"],
       PWD.TWOCO_nrmPos$Foci.nrm.pos[PWD.TWOCO_nrmPos$Foci.Type.nrm == "nrm.F2"])
#p-value = 0.5403
```

```{r fit.exp}
#fitting IFDs to expoential Distribution
#curBivData_PWD.melt
#make an IFD plot of Null.IFDs drawn from exponential
#curBivData_KAZ.melt2

#total Bivdata
KAZ.2COs <- KAZ.auto.man_BivData[KAZ.auto.man_BivData$hand.foci.count == 2,]
PWD.2COs <- PWD.auto.man_BivData[PWD.auto.man_BivData$hand.foci.count == 2,]

source("~./MLH1repo/src/CommonFunc_MLH1repo.R")
all.2CO <- add_IFD(all.2CO)
all.2CO <- droplevels(all.2CO)
all.2CO <- all.2CO[!(is.na(all.2CO$fileName) | all.2CO$fileName == ""), ]

all.2CO <- all.2CO[!(is.na(all.2CO$IFD1_PER) | all.2CO$IFD1_PER == ""), ]

require(vcd)
require(MASS)

# data generation
ex <- rexp(10000, rate = 1.85) # generate some exponential distribution
control <- abs(rnorm(10000)) # generate some other distribution

# estimate the parameters
fit1 <- fitdistr(ex, "exponential") 
fit2 <- fitdistr(control, "exponential")

fit.AP1 <- fitdistr(all.2CO$IFD1_PER, "exponential")

fit.PWD <- fitdistr(all.2CO$IFD1_PER[all.2CO$strain == "PWD"], "exponential")#change to gamma
fit.KAZ <- fitdistr(all.2CO$IFD1_PER[all.2CO$strain== "KAZ"], "exponential")

PWD.curve <- hist(all.2CO$IFD1_PER[all.2CO$strain == "PWD"], freq = FALSE, breaks = 100, xlim = c(0, quantile(ex, 0.99)))+
curve(dexp(x, rate = fit.PWD$estimate), from = 0, col = "red", add = TRUE)

KAZ.curve <- hist(all.2CO$IFD1_PER[all.2CO$strain == "KAZ"], freq = FALSE, breaks = 100, xlim = c(0, quantile(ex, 0.99)))+
curve(dexp(x, rate = fit.KAZ$estimate), from = 0, col = "red", add = TRUE)

ks.test(ex, "pexp", fit1$estimate) # p-value > 0.05 -> distribution not refused
ks.test(control, "pexp", fit2$estimate)

# plot a graph
hist(ex, freq = FALSE, breaks = 100, xlim = c(0, quantile(ex, 0.99)))+curve(dexp(x, rate = fit1$estimate), from = 0, col = "red", add = TRUE)

hist(all.2CO$IFD1_PER, freq = FALSE, breaks = 100, xlim = c(0, quantile(ex, 0.99)))+
curve(dexp(x, rate = fit.AP1$estimate), from = 0, col = "red", add = TRUE)

@@

@@
